Traditional agroforestry systems in Timor-Leste can store large amounts of carbon in both soil and biomass

### 2025-04-29 manuscript.Rmd
remove unused code

```{r bgc-estimation}
# root-to-shoot ratio allometry from Ledo et al., 2018
# use CWD values from Chave et al., 2014
# download from figshare https://figshare.com/articles/dataset/Root_Shoot_global_data_individual_trees/5144164?file=8754550
# rs <- readxl::read_excel("C:/Users/piponiot-laroche/Downloads/S1Database.xlsx",
#                          sheet = "DATA")
# rs$BGB_kg <- as.numeric(rs$BGB_kg)
# rs$wd <- as.numeric(rs$wd)
# rs$dbh2 <- rs$DBH_cm^2
# lm(log(BGB_kg/AGB_kg) ~ DBH_cm + dbh2 + wd,
#    data = subset(rs, !is.na(BGB_kg) & BGB_kg != 0))

data_sim_agc[, RS := exp(-1.2312 - 0.0215 * DIAM_130_CM +
  0.0002 * DIAM_130_CM^2 - 0.0007 * cwd)]
data_sim_agc[, BGC := RS * AGC]
```

@@

# limit of detectability: tree of 30 cm CBH, mean WD and height (for this DBH)
# LOD = computeAGB(D = 30/pi,
#                  WD = unique(data_wd$meanWD[data_wd$genus=="NR"]),
#                  H = data_tree[DIAM_130_CM == 30/pi, mean(HEIGHT)])
# data_sim_empty[iter != "mean", AGC := runif(sum(iter != "mean"), 0, LOD)]
# data_sim_empty[iter == "mean", AGC := LOD/2]
# RS = mean(data_sim_agc$RS[data_sim_agc$DIAM_130_CM==30/pi])
# data_sim_empty[, BGC := AGC * RS]

# data_sim_empty = melt(data_sim_empty, measure.vars = c("AGC", "BGC"))

@@

```{r add-missing-values}
data_soil[, Corg := `Corg\n`]
## add intermediate soil carbon in 10-20 cm depth under the assumption of an
# organic carbon content that decreases as a negative exponential of depth, we can deduce the carbon content at 10-20 cm with the following function: SOC[10-20] = SOC[0-10]*sqrt(SOC[20-30]/SOC[0-10])
data_soil <- merge(
  data_soil,
  data_soil[
    , .(
      Corg1020 = Corg[SAMPLE_DEPTH == "0-10"] *
        sqrt(Corg[SAMPLE_DEPTH == "20-30"] / Corg[SAMPLE_DEPTH == "0-10"])
    ),
    .(N_PLOT)
  ]
)

@@

## error propagation using a Monte Carlo method -------------
data_sim_soil <- data_soil[
  , .(
    mfine = c(Sample_DRY, rnorm(1000, Sample_DRY, Sample_DRY * 0.1)), # 10% error on fine soil mass
    Corg = c(Corg, rnorm(1000, Corg, Corg * 0.12)), # 12% error on C content measurement
    iter = c("mean", paste0("V", 1:1000))
  ),
  .(N_PLOT, SAMPLE_DEPTH, h1, h0)
]

@@

<!-- ```{r tab.id = "anova", results = "show", tab.cap = "Results of the two 2-way ANOVAs with log-transformed median AGC and SOC as dependent variables, and AFS and site as independent variables. The p-value gives the probability of the means of the categories of each independent variable being the same. Bold p-values are lower than 0.05, and the mean difference between groups is thus considered significantly different than zero."} -->

<!-- anova_table$factor = factor(anova_table$factor) -->

<!-- levels(anova_table$factor) = c("AFS", "site") -->

<!-- flextable(anova_table, col_keys = c("variable", "factor", "pvalue"),  -->

<!--           cwidth = c(1, 1, 0.8)) |>  -->

<!--   bold(i = anova_table$pvalue < 0.05, j = 2:3) |>  -->

<!--   set_header_labels(values = c("Dependent variable", "Independent variable", "p-value")) |>  -->

<!--   merge_at(i = 1:2, j = 1) |> merge_at(i = 3:4, j = 1) |>  -->

<!--   fix_border_issues() |> hline(i=2) -->

<!-- ``` -->

>>>>

```{r bgc-estimation}
# root-to-shoot ratio allometry from Ledo et al., 2018
# use CWD values from Chave et al., 2014
data_sim_agc[, RS := exp(-1.2312 - 0.0215 * DIAM_130_CM +
  0.0002 * DIAM_130_CM^2 - 0.0007 * cwd)]
data_sim_agc[, BGC := RS * AGC]
```

@@

@@

```{r add-missing-values}
data_soil[, Corg := `Corg\n`]
## add intermediate soil carbon in 10-20 cm depth under the assumption of an
# organic carbon content that decreases as a negative exponential of depth, 
# we can deduce the carbon content at 10-20 cm with the following function: 
# SOC[10-20] = SOC[0-10]*sqrt(SOC[20-30]/SOC[0-10])
data_soil <- merge(
  data_soil,
  data_soil[
    , .(
      Corg1020 = Corg[SAMPLE_DEPTH == "0-10"] *
        sqrt(Corg[SAMPLE_DEPTH == "20-30"] / Corg[SAMPLE_DEPTH == "0-10"])
    ),
    .(N_PLOT)
  ]
)

@@

## error propagation using a Monte Carlo method -------------
data_sim_soil <- data_soil[
  , .(
    # 10% error on fine soil mass
    mfine = c(Sample_DRY, rnorm(1000, Sample_DRY, Sample_DRY * 0.1)), 
    # 12% error on C content measurement
    Corg = c(Corg, rnorm(1000, Corg, Corg * 0.12)), 
    iter = c("mean", paste0("V", 1:1000))
  ),
  .(N_PLOT, SAMPLE_DEPTH, h1, h0)
]

@@
